---
title: ""
subtitle: ""
author:
  - name: "Jürgen Schneider"
    email: "ju.schneider@dipf.de"
    affiliation: "DIPF"
    correspondence: true
date: "`r Sys.Date()`" # inserts the date of compiling
editor: source
execute:
  echo: true
  warning: false
  message: false
  cache: false # true will prevent embed-resources
format: 
  html:
    theme: ceruleanc
    number-sections: true
    fontsize: 0.85em
    toc: true
    toc-location: left
    toc-depth: 3
    embed-resources: true # will make standalone html file
    code-fold: true
    code-tools: true
    code-link: true
editor_options: 
  chunk_output_type: console
---

```{r packages}
#| echo: false
#| eval: true

library(rio)
library(tidyverse)
library(lavaan)
library(brms)
```


```{r import}
df <- rio::import("data/n9412_Rotation3_Datensatz_JGO.sav")

```

# Hypotheses
As preregistered on [aspredicted.org/JX3_XDW](https://aspredicted.org/JX3_XDW), our Hypotheses were:

1a: No relation of teachers' practical experience in school with their inquiry habit of mind.  
1b: No relation of teachers' transfer beliefs of theory and practice with their inquiry habit of mind.  
  
2a: The higher teachers' application of knowledge and skills, the higher teachers' inquiry habit of mind.  
2b: The higher teachers' selection beliefs of theory and practice, the higher teachers' inquiry habit of mind.  
2c: The higher teachers' enrichment beliefs of theory and practice, the higher teachers' inquiry habit of mind.  
  
*Exploratory:*  
3a: The higher the teachers' metareflective stance, the higher teachers' inquiry habit of mind.  
3b: The higher teachers' relationing beliefs of theory and practice, the higher teachers' inquiry habit of mind.



metareflective stance  
application of knowledge and skills

# Measurement Models

## Inquiry Habit of Mind

```{r}
model_ihom <- '
              InquiryHabit =~ f3_1 + f3_2 + f3_3 + f3_4 + f3_5 + f3_6 + f3_7 + f3_8
              '

fit_ihom <- lavaan::cfa(model_ihom, data = df, std.lv = TRUE)
summary(fit_ihom, fit.measures = TRUE, standardized = TRUE)
lambdas_ihom <- parameterEstimates(fit_ihom)[1:8, "est"]   # Extract weights from model
```

## Beliefs: Transfer

```{r}
model_b_trans <- '
                 transfer =~ f5_1 + f5_2 + f5_3 + f5_5
                 '

fit_b_trans <- lavaan::cfa(model_b_trans, data = df, std.lv = TRUE)
summary(fit_b_trans, fit.measures = TRUE, standardized = TRUE)

lambdas_b_trans <- parameterEstimates(fit_b_trans)[1:4, "est"]   # Extract weights from model
```


## Beliefs: Selection

```{r}
model_b_selec <- '
                 selection =~ f5_6 + f5_8 + f5_9 + f5_10
                 '

fit_b_selec <- lavaan::cfa(model_b_selec, data = df, std.lv = TRUE)
summary(fit_b_selec, fit.measures = TRUE, standardized = TRUE)

lambdas_b_selec <- parameterEstimates(fit_b_selec)[1:4, "est"]   # Extract weights from model
```

## Beliefs: Enrichment

```{r}
model_b_enric <- '
                 enrichment =~ f5_11 + f5_12 + f5_13 + f5_14
                 '

fit_b_enric <- lavaan::cfa(model_b_enric, data = df, std.lv = TRUE)
summary(fit_b_enric, fit.measures = TRUE, standardized = TRUE)

lambdas_b_enric <- parameterEstimates(fit_b_enric)[1:4, "est"]   # Extract weights from model
```

## Beliefs: Relationing

```{r}
model_b_relat <- '
                 relationing =~ f5_16 + f5_17 + f5_18 + f5_19
                 '

fit_b_relat <- lavaan::cfa(model_b_relat, data = df, std.lv = TRUE)
summary(fit_b_relat, fit.measures = TRUE, standardized = TRUE)

lambdas_b_relat <- parameterEstimates(fit_b_relat)[1:4, "est"]   # Extract weights from model
```


# Factor scores


```{r}
df <- df |>
  dplyr::mutate(inqiry_habit = rowMeans(data.frame(lambdas_ihom[1]*f3_1, # Use weights from model 
                                                   lambdas_ihom[2]*f3_2, # to compute factor
                                                   lambdas_ihom[3]*f3_3, # score according to
                                                   lambdas_ihom[4]*f3_4, # measurement model
                                                   lambdas_ihom[5]*f3_5, 
                                                   lambdas_ihom[6]*f3_6, 
                                                   lambdas_ihom[7]*f3_7, 
                                                   lambdas_ihom[8]*f3_8), 
                                        na.rm = TRUE),
                beliefs_transfer = rowMeans(data.frame(lambdas_b_trans[1]*f5_1,  
                                                       lambdas_b_trans[2]*f5_2,  
                                                       lambdas_b_trans[3]*f5_3,  
                                                       lambdas_b_trans[4]*f5_5),  
                                            na.rm = TRUE), 
                beliefs_selectio = rowMeans(data.frame(lambdas_b_selec[1]*f5_6,  
                                                       lambdas_b_selec[2]*f5_8,  
                                                       lambdas_b_selec[3]*f5_9,  
                                                       lambdas_b_selec[4]*f5_10), 
                                            na.rm = TRUE), 
                beliefs_enrichme = rowMeans(data.frame(lambdas_b_enric[1]*f5_11, 
                                                       lambdas_b_enric[2]*f5_12, 
                                                       lambdas_b_enric[3]*f5_13, 
                                                       lambdas_b_enric[4]*f5_14), 
                                            na.rm = TRUE), 
                beliefs_relation = rowMeans(data.frame(lambdas_b_relat[1]*f5_16, 
                                                       lambdas_b_relat[2]*f5_17, 
                                                       lambdas_b_relat[3]*f5_18, 
                                                       lambdas_b_relat[4]*f5_19), 
                                            na.rm = TRUE),
                experience = jahre
                )
```




# Analyses

## H1a

1a: No relation of teachers' practical experience in school with their inquiry habit of mind.  

```{r}
fit_h1a <- brm(
  formula = inqiry_habit ~ experience,
  data = df,
  prior = prior(student_t(10, 0, .5), # fairly informative prior for slope
                coef = experience), 
  sample_prior = 'yes', # (necessary for calculating BFs with Savage-Dickey)
  iter = 20000,
  silent = 2, # spare me the messages of compiler and sampler
  refresh = 0 # spare me the messages of compiler and sampler
  )

summary(fit_h1a)

# hypothesis(fit_h1a, "abs(experience) < .1")
hypothesis(fit_h1a, "experience = 0")
```

